---
title: "DeconfoundedGroupDifference_Tutorial"
author: "Benjamin Risk"
date: "8/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up random seed and multicore
```{r}
options(mc.cores=8)
getOption("mc.cores")
seed = 123
set.seed(seed, "L'Ecuyer-CMRG")
```

## Simulate data

Here, we will create a variable X1 that will be driving the confounding between usability and functional connectivity. The idea is to create a variable similar to a measure of ASD severity. It is equal to zero when A=0 and is log normal when A=1. We also create some additional covariates to make the estimation a little harder. In this example, there is bias in the ASD functional connectivity but not in the TD. 

We create a huge dataset that is used to calculate $E^*[Y(1)|A=0]$ and $E^*[Y(1)|A=1]$, then we also create a sample from this "population" that is then used to estimate $E[E[Y|\Delta=1,A=0,W]|A=0]$ and $E[E[Y|\Delta=1,A=1,W]|A=1]$. 

```{r simdata1}
p=10 # number of covariates
n1 = 100000 # number of observations to obtain the "true" functional connectivity; needs to be large
n2 = 550 # number of observations in the "sample"; n2<=n1

A = rbinom(n1,1,0.25) # diagnosis

X1 = A*exp(rnorm(n1,sd=0.4)+2) # equal to 0 for A=0, log normal for A=1
#hist(X1)
W = cbind(X1,matrix(rnorm(n1*(p-1)),nrow=n1))

gn.true = plogis(2-0.2*X1) # intercept: exp(beta0)/(1+exp(beta0)) is the proportion of A=0 usable

quantile(gn.true,0.025) # note: helps to choose parameters so that this is not too close to 0 or 1
quantile(gn.true,0.975)
Delta = rbinom(n=n1,size=1,prob = gn.true)
min(gn.true[Delta==1])

# Usable in ASD:
mean(Delta[A==1])
# Usable in TD:
mean(Delta[A==0])

# check the difference in mean of X1 in all data versus usable.
# This will influence the degree of confounding:
mean(X1[A==1])
mean(X1[A==1 & Delta==1])

# Simulate functional connectivity:
# In this set up, conditional effect of asd positive, but marginal negative:
betas_Qbar = c(-0.2,rep(0,p-1),1.4) 
xmat=cbind(W,A)
Y = xmat%*%betas_Qbar+rnorm(n1,sd=0.2)

# Calculate the "true" ASD fconn and "true" TD:
(ASD.true = mean(Y[A==1]))
(TD.true = mean(Y[A==0]))

# These are the biased means resulting from confounding with usability:
mean(Y[A==1 & Delta==1])
mean(Y[A==0 & Delta==1])

sample.i = sample(n1,n2,replace=FALSE)
Y.sample = Y[sample.i]
Delta.sample = Delta[sample.i]
A.sample = A[sample.i]
W.sample = W[sample.i,]


# the best estimate of deconfounded group difference we can expect given limited sample size:
# this reflects sampling variability
mean(Y.sample[A.sample==1])
mean(Y.sample[A.sample==0])

```

## Fit propensity model using superlearner:
```{r, echo=FALSE, message=FALSE}
library(drtmle)
library(SuperLearner)
library(earth)
library(quadprog)
library(gam)
library(nloptr)
library(future)
library(future.apply)
library(xgboost)
library(ranger)
library(visdat)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(e1071)
library(glmnet)
```

Estimate propensities (gn) using all data:

```{r message=FALSE}
my.SL.libs = c("SL.earth","SL.glmnet","SL.gam","SL.glm","SL.ranger","SL.ridge","SL.step","SL.step.interaction","SL.svm","SL.xgboost","SL.mean")

(gn.est = mcSuperLearner(Y = Delta.sample, X = data.frame(cbind(W.sample,A.sample)), family=binomial(link='logit'),SL.library = my.SL.libs, cvControl = list(V = 10), method='method.AUC')) # 10-fold CV

cor(gn.est$SL.predict,gn.true[sample.i])
```

It's okay that you get warnings for ridge (which is not set up for logistic regression) and for support vector machines. The other learners should run without warning. 

## Fit outcome model using superlearner:
Estimate outcome model using usable data. Note: drtlme::tmp_method.CC_LS adjusts the tolerances as recommended by Dr. @benkbios:

```{r}
(Qbar.est =   mcSuperLearner(Y = Y.sample[Delta.sample==1], X=data.frame(cbind(W.sample,A.sample)[Delta.sample==1,]), family=gaussian(), SL.library = my.SL.libs, cvControl = list(V = 10), method = drtmle:::tmp_method.CC_LS))
```      

Predict outcome for all usable and unusable data:
```{r}
Qbar.predict = predict(Qbar.est, newdata = data.frame(cbind(W.sample,A.sample)))[[1]]
cor(Y.sample,Qbar.predict)
```

## Estimate the deconfounded group difference:

```{r}
# ASD:
mean_fconn_asd.SL <- drtmle(Y = Y.sample[A.sample==1],
                              A = Delta.sample[A.sample==1], # apologies for the notation conflict -- use Delta here
                              W = NULL, # does not do anything with user-input propensities and outcomes
                              a_0 = 1, # set this to one to correspond to Delta=1
                              Qn = list(Qbar.predict[A.sample==1]), # pass in fitted outcome values
                              gn = list(gn.est$SL.predict[A.sample==1]), # pass in fitted propensities
                              SL_Qr = "SL.npreg", # uses non-parametric regression in the drtmle step
                              SL_gr = "SL.npreg",
                              maxIter = 1
                            )

# TD:
mean_fconn_td.SL <- drtmle(Y = Y.sample[A.sample==0],
                              A = Delta.sample[A.sample==0], 
                              W = NULL, 
                              a_0 = 1, 
                              Qn = list(Qbar.predict[A.sample==0]),
                              gn = list(gn.est$SL.predict[A.sample==0]), 
                              SL_Qr = "SL.npreg",
                              SL_gr = "SL.npreg",
                              maxIter = 1
                            )

deconfounded.diff = mean_fconn_asd.SL[[1]]$est - mean_fconn_td.SL[[1]]$est

# test the difference between groups:
z.deconfounded.diff = deconfounded.diff/sqrt(mean_fconn_asd.SL[[1]]$cov+mean_fconn_td.SL[[1]]$cov)
```

## Compare the true difference, deconfounded difference, and the naive approach:

```{r}

ASD.true - TD.true

# the best we can expect given limited sample size:
mean(Y.sample[A.sample==1])-mean(Y.sample[A.sample==0])

# our estimate:
deconfounded.diff

# naive estimate: 
(naive.diff = mean(Y.sample[A.sample==1 & Delta.sample==1]) - mean(Y.sample[A.sample==0 & Delta.sample==1]))

# hypothesis testing:
# h_0: no difference between asd and td
z.deconfounded.diff
2*(1-pnorm(abs(z.deconfounded.diff)))

t.test(Y.sample[A.sample==1 & Delta.sample==1],Y.sample[A.sample==0 & Delta.sample==1])

```
